---
title: "cocor, Post"
output: html_document
---

cocor - comparing correlations, 1.1-2, http://comparingcorrelations.org

raghunathan1996 is a common optimization of Pearson-Filon Z statistic for comparing dependent but non-overlapping correlations

NOTE: must manually set number of observations in cocor code below at this time

Load relevant libraries (e.g. gdata package to enable xls reading)
```{r}
library(gdata)
library(nlme)
library(reshape2)
library(lme4)
library(lmerTest)
```

load package
```{r}
require(cocor) 
```

set working directory to where data are
```{r}
setwd("C:/Users/Thackery/Dropbox/Work transfer/ORE/R_analysis")

```

Import excel file of interest (there are assumptions about formatting here...)
```{r}
testdata = read.xls("testfile4.xls")
head(testdata)
summary(testdata)
```

Tell R specifically to make the sub id column a "factor", because it will likely import them as integers otherwise
```{r factor_subject}
testdata$sub = factor(testdata$sub)
str(testdata)

```

Create correlation matrix of numeric (non factor or character) entries in data. Skip missing entries (NA)
```{r}
COR <- cor(testdata[sapply(testdata, is.numeric)], use="pairwise.complete.obs")
COR
```

```{r}
cocor.dep.groups.nonoverlap(r.jk=COR["In_grp","inda"], r.hm=COR["Out_grp","outda"], r.jh=COR["In_grp","Out_grp"], r.jm=COR["In_grp","outda"], r.kh=COR["Out_grp","inda"], r.km=COR["inda","outda"], n=22, alternative="two.sided", alpha=0.05, conf.level=0.95, null.value=0)
```




