---
title: "Corr, Post"
author: "Thackery Brown"
date: "12/18/2015"
#output: pdf_document
---

Load relevant libraries (e.g. gdata package to enable xls reading)
```{r}
library(gdata)
library(nlme)
library(reshape2)
library(lme4)
library(lmerTest)
library(Hmisc)
```

set working directory to where data are
```{r}
setwd("C:/Users/Thackery/Dropbox/Work transfer/ORE/R_analysis")

```


Import excel file of interest (there are assumptions about formatting here...)
```{r}
testdata = read.xls("testfile3.xls")
head(testdata)
summary(testdata)
```

Tell R specifically to make the sub id column a "factor", because it will likely import them as integers otherwise
```{r factor_subject}
testdata$sub = factor(testdata$sub)
str(testdata)

```

Create correlation matrix of numeric (non factor or character) entries in data. Skip missing entries (NA)
```{r}
COR <- cor(testdata[sapply(testdata, is.numeric)], use="pairwise.complete.obs")
COR
```


re-run using rcorr to get p values
```{r}
x <- testdata[sapply(testdata, is.numeric)]
rcorr(as.matrix(x))
```


