---
title: "Mixedfx of d' by race"
author: "Thackery Brown"
date: "3/24/2016"
#output: pdf_document
---

Load relevant libraries (e.g. gdata package to enable xls reading)
```{r}
library(gdata)
library(nlme)
library(reshape2)
library(lme4)
library(lmerTest)
library(car) # for changing the type of ANOVA table
```

set working directory to where data are
```{r}
setwd("C:/Users/Thackery/Dropbox/Work transfer/ORE/R_analysis")

```


Import excel file of interest (there are assumptions about formatting here...)
```{r}
testdata = read.xls("testfileEAvsAA.xls")
head(testdata)
summary(testdata)
```

Tell R specifically to make the sub id column a "factor", because it will likely import them as integers otherwise
```{r factor_subject}
testdata$sub = factor(testdata$sub)
str(testdata)
```
Now let's reformat the data into "long" format for repeated-measures analysis
```{r}
#myrepeatedmeasures<-make.rm(constant=c('sub'),repeated=c('score1','score2'),data=testdata)
myrepeatedmeasures <- melt(testdata) #melt(testdata, id=c("sub")) 
```

View data (repdat = variable of analysis, contrasts = repetition labels, cons.col = subjects)
```{r}
head(myrepeatedmeasures)
tail(myrepeatedmeasures)
str(myrepeatedmeasures)
```
set up contrasts

```{r}
contrasts(myrepeatedmeasures$race) = c(-1,1); contrasts(myrepeatedmeasures$race)

contrasts(myrepeatedmeasures$variable) = c(1,-1); contrasts(myrepeatedmeasures$variable)

```

And crunch the mixed-effects model

### mixed effects, most complex
```{r}
rs1 = lmer(value ~ race * variable + (1|sub), data=myrepeatedmeasures)
summary(rs1)

```

### anova from most complex using type 3 
```{r}
anova(rs1)

```

### anova from most complex using type 2

```{r}
Anova(rs1, type='II')

```

### simplified model 


```{r}
rs2 = lmer(value ~ race + variable + (1|sub), data=myrepeatedmeasures)
anova(rs1, rs2) # rs1 isn't any better
summary(rs2)
```

### simplified further by removing race as a factor

```{r}
rs3 = lmer(value ~ variable + (1|sub), data=myrepeatedmeasures)
anova(rs2, rs3) # rs2 isn't any better than this simple model
summary(rs3)
```


### lastly, AOV version
This should match results w/ANOVA w/type II ANOVA table:
```{r}
fit <- aov(value~(variable*race)+Error(sub/(variable))+(race), data=myrepeatedmeasures)
summary(fit)

```



