---
title: "Necos, Bilateral, two hippoROIs*3 conds"
author: "Thackery Brown"
date: "06/28/2016"
#output: pdf_document
---

Load relevant libraries (e.g. gdata package to enable xls reading)
```{r}
library(gdata)
library(nlme)
library(reshape2)
library(lme4)
library(lmerTest)
```

set working directory to where data are
```{r}
setwd("C:/Users/Thackery/Documents/work/necos/R_analysis")

```


Import excel file of interest (there are assumptions about formatting here...)
```{r}
testdata = read.xls("testfile1b.xls")
head(testdata)
summary(testdata)
```

Tell R specifically to make the sub id column a "factor", because it will likely import them as integers otherwise
```{r factor_subject}
testdata$sub = factor(testdata$sub)
str(testdata)
```

Get expected paired difference significance using paired t-test

### T-Test
```{r}
t.test(testdata$Tail, testdata$Body, paired=TRUE)
```

Now let's reformat the data into "long" format for repeated-measures analysis
```{r}
#myrepeatedmeasures<-make.rm(constant=c('sub'),repeated=c('score1','score2'),data=testdata)
myrepeatedmeasures <- melt(testdata) #melt(testdata, id=c("sub")) 

```
View data (repdat = variable of analysis, contrasts = repetition labels, cons.col = subjects)
```{r}
head(myrepeatedmeasures)
tail(myrepeatedmeasures)
str(myrepeatedmeasures)
```

Mixed effect model approach to repeated-measures analysis:
```{r}
str(myrepeatedmeasures)
contrasts(myrepeatedmeasures$variable) = c(1,-1); contrasts(myrepeatedmeasures$variable)
contrasts(myrepeatedmeasures$cond) = cbind(stratVSother = c(-.5,-.5,1),
                                           revVSstay = c(1,-1,0)); contrasts(myrepeatedmeasures$cond)
contrasts(myrepeatedmeasures$hemisphere) = c(1,-1); contrasts(myrepeatedmeasures$hemisphere)

# even more complex model
res3 = lmer(value ~ (variable * cond) * hemisphere + (1|sub), data=myrepeatedmeasures)
summary(res3)
anova(res3)

# even more complex model
res4 = lmer(value ~ (variable * cond) * hemisphere + (1 + variable|sub), data=myrepeatedmeasures)
summary(res4)
anova(res4)

# even more complex model
res5 = lmer(value ~ (variable * cond) * hemisphere + (1 + variable + cond|sub), data=myrepeatedmeasures)
summary(res5)
anova(res5)

# more complex model
#res6 = lmer(value ~ variable * cond + variable * hemisphere + variable*cond*hemisphere + (1 + variable + cond + hemisphere|sub), data=myrepeatedmeasures)
res6 = lmer(value ~ (variable * cond) * hemisphere + (1 + variable + cond + hemisphere|sub), data=myrepeatedmeasures)
summary(res6)
anova(res6)

# most complex model
res7 = lmer(value ~ (variable * cond) * hemisphere + (1 + variable + cond + hemisphere + variable:cond|sub), data=myrepeatedmeasures)
summary(res7)
anova(res7)

# determine which model is best (take simplest when there is no sig Chi Sq)
anova(res3, res4, res5, res6, res7, refit=FALSE)
#coef(res6)

# most complex model effects just in tail
# contrasts(myrepeatedmeasures$variable) = c(0,1); contrasts(myrepeatedmeasures$variable)
# res6 = lmer(value ~ variable * cond + variable * hemisphere + variable*cond*hemisphere + (1 + variable + cond + hemisphere|sub), data=myrepeatedmeasures)
# summary(res6)
# anova(res6)


# most complex model effects just in body
# contrasts(myrepeatedmeasures$variable) = c(1,0); contrasts(myrepeatedmeasures$variable)
# res6 = lmer(value ~ variable * cond + variable * hemisphere + variable*cond*hemisphere + (1 + variable + cond + hemisphere|sub), data=myrepeatedmeasures)
# summary(res6)
# anova(res6)

```

And crunch the univariate repeated-measures ANOVA

### AOV
```{r}
# rs_aov = aov(value~(variable*cond)+Error(sub/(variable*cond)),myrepeatedmeasures)
# summary(rs_aov)
#drop1(rs_aov,~.,test="F")
```
### paired T-test for specific factor
Now that we reshaped the data, the t-test code format changes
First, filter data to factor level of interest

```{r}
Stayonly <- subset(myrepeatedmeasures, cond=="Stay")
Revonly <- subset(myrepeatedmeasures, cond=="Rev")

# Tailonly <- myrepeatedmeasures[myrepeatedmeasures$variable == 'Tail',] #subset myrepeatedmeasures with indexing
# Tailonly_revstay <- Tailonly[Tailonly$cond %in% c('Stay', 'Rev'),] #subset Tailonly with indexing using a string of indices
# Tailonly_stratvrev <- Tailonly[Tailonly$cond %in% c('Strat', 'Rev'),] #subset Tailonly with indexing using a string of indices
# Tailonly_stratvstay <- Tailonly[Tailonly$cond %in% c('Strat', 'Stay'),] #subset Tailonly with indexing using a string of indices
# 
# Bodyonly <- myrepeatedmeasures[myrepeatedmeasures$variable == 'Body',] #subset myrepeatedmeasures with indexing
# Bodyonly_revstay <- Bodyonly[Bodyonly$cond %in% c('Stay', 'Rev'),] #subset Tailonly with indexing using a string of indices
# Bodyonly_stratvrev <- Bodyonly[Bodyonly$cond %in% c('Strat', 'Rev'),] #subset Tailonly with indexing using a string of indices
# Bodyonly_stratvstay <- Bodyonly[Bodyonly$cond %in% c('Strat', 'Stay'),] #subset Tailonly with indexing using a string of indices
```

Then conduct t-tests

```{r}
# t.test(value ~ cond, Tailonly_revstay, paired=TRUE)
# t.test(value ~ cond, Tailonly_stratvrev, paired=TRUE)
# t.test(value ~ cond, Tailonly_stratvstay, paired=TRUE)
# 
# t.test(value ~ cond, Bodyonly_revstay, paired=TRUE)
# t.test(value ~ cond, Bodyonly_stratvrev, paired=TRUE)
# t.test(value ~ cond, Bodyonly_stratvstay, paired=TRUE)

```

