---
title: "simple_repeatedmeasures_2way"
author: "Thackery Brown"
date: "12/18/2015"
#output: pdf_document
---

Load relevant libraries (e.g. gdata package to enable xls reading)
```{r}
library(gdata)
library(nlme)
library(reshape2)
library(lme4)
library(lmerTest)
```

Import excel file of interest (there are assumptions about formatting here...)
```{r}
testdata = read.xls("testfile2.xls")
head(testdata)
summary(testdata)
```

Tell R specifically to make the sub id column a "factor", because it will likely import them as integers otherwise
```{r factor_subject}
testdata$sub = factor(testdata$sub)
str(testdata)
```

Get expected paired difference significance using paired t-test

### T-Test
```{r}
t.test(testdata$score1, testdata$score2, paired=TRUE)
```

Now let's reformat the data into "long" format for repeated-measures analysis
```{r}
#myrepeatedmeasures<-make.rm(constant=c('sub'),repeated=c('score1','score2'),data=testdata)
myrepeatedmeasures <- melt(testdata) #melt(testdata, id=c("sub")) 
```

View data (repdat = variable of analysis, contrasts = repetition labels, cons.col = subjects)
```{r}
head(myrepeatedmeasures)
tail(myrepeatedmeasures)
str(myrepeatedmeasures)
```

And crunch the univariate repeated-measures ANOVA

### AOV
```{r}
rs_aov = aov(value~(variable*network)+Error(sub/(variable*network)),myrepeatedmeasures)
summary(rs_aov)
```
### paired T-test for specific factor
Now that we reshaped the data, the t-test code format changes
First, filter data to factor level of interest

```{r}
DANonly <- subset(myrepeatedmeasures, network=="DAN")
```

Then conduct t-test

```{r}
t.test(value ~ variable, DANonly, paired=TRUE)
```


### Equivalent from Linear Mixed Effects package
...coming soon