---
title: "simple_repeatedmeasures"
author: "Thackery Brown"
date: "11/06/2014"
#output: pdf_document
---

Load relevant libraries (e.g. gdata package to enable xls reading)
```{r}
library(gdata)
library(nlme)
library(reshape2)
library(lme4)
library(lmerTest)
```

Import excel file of interest (there are assumptions about formatting here...)
```{r}
testdata = read.xls("testfile.xls")
head(testdata)
summary(testdata)
```

Tell R specifically to make the sub id column a "factor", because it might import them as integers otherwise
```{r factor_subject}
testdata$sub = factor(testdata$sub)
str(testdata)
```

Get expected paired difference significance using paired t-test
### T-Test
```{r}
t.test(testdata$score1, testdata$score2, paired=TRUE)
```

Now let's reformat the data into "long" format for repeated-measures analysis
```{r}
#myrepeatedmeasures<-make.rm(constant=c('sub'),repeated=c('score1','score2'),data=testdata)
myrepeatedmeasures <- melt(testdata, id=c("sub")) 
```

View data (repdat = variable of analysis, contrasts = repetition labels, cons.col = subjects)
```{r}
head(myrepeatedmeasures)
tail(myrepeatedmeasures)
str(myrepeatedmeasures)
```

And crunch the univariate repeated-measures ANOVA

### AOV
```{r}
rs_aov = aov(value~variable+Error(sub/variable),myrepeatedmeasures)
summary(rs_aov)
```

### Equivalent from Linear Mixed Effects package
```{r}
contrasts(myrepeatedmeasures$variable)
rs_lme = lme(value ~ variable, data = myrepeatedmeasures, random = ~ 1 | sub) 
summary(rs_lme)

# Now, use contrast coding
contrasts(myrepeatedmeasures$variable) = c(-1,1)
contrasts(myrepeatedmeasures$variable)
rs_lme_effect = lme(value ~ variable, data = myrepeatedmeasures, random = ~ 1 | sub) 
summary(rs_lme_effect)
anova(rs_lme_effect)
```

### LMER
```{r}
rs_lmer = lmer(value ~ variable + (1|sub), data = myrepeatedmeasures)
summary(rs_lmer)
anova(rs_lmer)
```

### Comparison across functions
```{r}
summary(rs_aov)
anova(rs_lme_effect)
anova(rs_lmer)
```
